---
title: "reprex_new_standalone_overwriting_cites"
format:
    pdf:
        keep-md: true
    html:
        keep-md: true
        keep-tex: true
    docx:
        keep-md: true
bibliography: "grateful-refs.bib"
---
(table [-@tbl-PackageVersions2])
This is a playground for Quarto `r quarto::quarto_version()`.
Standalone file, rendered in RStudio via `Render Current Document`.
<!-- follow-up, cf. comment https://github.com/quarto-dev/quarto-cli/discussions/8580#discussioncomment-8380758 -->
---


```{r}
library(grateful)
library(knitr)
library(sessioninfo)
library(formatdown)
library(processx)
library(quarto)
library(renv)
library(rmarkdown)
library(tidyverse)
library(yaml)
cites <- cite_packages(
    output = "table", ,
    out.dir = ".",
    cite.tidyverse = TRUE,
    pkgs = "All",
    include.RStudio = TRUE,
    dependencies = FALSE,
    omit = c("base", "formatdown")
)
print(cites)
typeof(cites)
```

---

caption via Cell label `#| tbl-cap`
<!-- caption via `knitr(...,caption = "caption")` -->


```{r}
#| label: tbl-PackageVersions2
#| echo: FALSE
#| warning: FALSE
#| cache: FALSE
#| tbl-cap: "caption via tbl-cap"
# kable(cites,caption = "caption via kable")
kable(cites)
```

--- 

manual table copied from the `.md`-intermediate: the cites themselves _can_ get rendered correctly.

|Package     |Version |Citation                                       |
|:-----------|:-------|:----------------------------------------------|
|base        |4.3.2   |@base                                          |
|formatdown  |0.1.2   |@formatdown                                    |
|knitr       |1.45    |@knitr2014; @knitr2015; @knitr2023             |
|processx    |3.8.3   |@processx                                      |
|quarto      |1.3     |@quarto                                        |
|renv        |1.0.3   |@renv                                          |
|rmarkdown   |2.25    |@rmarkdown2018; @rmarkdown2020; @rmarkdown2023 |
|sessioninfo |1.2.2   |@sessioninfo                                   |
|tidyverse   |2.0.0   |@tidyverse                                     |
|yaml        |2.3.8   |@yaml                                          |


---

```{r}
sessionInfo()
```
